\textbf{Proposal for bachelor thesis}\\ Exploration of the influence of graph parameters on the generalization error of Graph Neural Networks

### 2025-02-03 paper/chapters/experimentalstudy.tex
Update experimentalstudy.tex to correct dataset count and clarify GATv2 terminology

I list information about the 50 datasets used in the experiment in the appendix~\ref{sec:}.

@@

\subsection{Models}\label{sec:models}
In the experiment, I plan to use different GNN layers in the model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}. The GCN model is shown in the appendix. The GCN model consists of four GCN layers, each followed by a ReLU activation function. The output of the last GCN layer is passed through a global mean pooling layer, followed by two fully connected layers.

>>>>

I list information about the 49 datasets used in the experiment in the appendix~\ref{sec:TODO}.

@@

\subsection{Models}\label{sec:models}
In the experiment, I plan to use different GNN layers in the model, including Graph Convolutional Networks(GCN)~\cite{kipf2016semi}, Graph Attention Networks(GAT)~\cite{velickovic2020pointer}, Graph Attention Networks v2(GATv2)~\cite{brody2021attentive}, Simplified Graph Convolution(SGC)~\cite{wu2019simplifying}, and Message Passing Neural Networks(MPNN)~\cite{gilmer2017neural}. The GCN model is shown in the appendix. The GCN model consists of four GCN layers, each followed by a ReLU activation function. The output of the last GCN layer is passed through a global mean pooling layer, followed by two fully connected layers.
